Data preparation report

### 2023-06-09 00_dataPrepReport.Rmd
fixed battery/ppd filter, and removed summer 2020

## Remove days on which individuals don't have at least 10 points.
before <- seasons
seasons <- map(seasons, ~.x %>%
                 group_by(Nili_id, dateOnly) %>%
                 filter(n() >= 10) %>% # hard-coding the 10 in here so it doesn't accidentally get changed.
                 ungroup())
after <- seasons

@@

indivsToKeep <- map2(.x = seasons, .y = durs, ~.x %>%
                       st_drop_geometry() %>%
                       group_by(Nili_id) %>%
                       summarize(nDaysTracked = length(unique(dateOnly)),
                                 propDaysTracked = nDaysTracked/.y) %>%
                       filter(propDaysTracked >= 0.33) %>% # XXX ask Orr if this should be percentage vs. number of days, given the different season lengths. (email)
                       pull(Nili_id))

@@

>>>>

## Keep days with more than 10 points, or with fewer than 10 if the minimum battery charge that day is >50%
before <- seasons
seasons <- map(seasons, ~.x %>%
                 group_by(Nili_id, dateOnly) %>%
                 filter(n() >= 10 | (n() < 10 & min(battery_charge_percent, na.rm = T) > 50)) %>%
                 ungroup())
after <- seasons

@@

indivsToKeep <- map2(.x = seasons, .y = durs, ~.x %>%
                       st_drop_geometry() %>%
                       group_by(Nili_id) %>%
                       summarize(nDaysTracked = length(unique(dateOnly)),
                                 propDaysTracked = nDaysTracked/.y) %>%
                       filter(nDaysTracked >= 30) %>%
                       pull(Nili_id))

@@

```{r include = T, echo = F}
df

## Now I notice that season 1, Summer 2020, doesn't have enough individuals. Let's remove it--we're going to have to anyway.
seasons <- seasons[-1]
```
